Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex

Auto-tuning techniques attempt to find a good solution among a huge space of
available system configurations. However, in practice auto-tuning is limited
to only the configuration tunables that the storage system exposes and can be
overwhelmed with too many parameters.  For instance, auto-tuning may be
capable of identifying instances in which new data layouts would benefit a
workload, but unless the system can provide such a transformation, the option
is left off the table.  Starfish~\cite{herodotou:cidr2011-starfish} made
an attempt at this for Hadoop but this technique would need to severely limit
the space of parameters in order to be feasible, similar to the approach used in~\cite{behzad:sc2013-autotuning}.

@@

The distributed metadata service in Ceph provides clients with a POSIX file
system abstraction. Distributed file systems are complex, but fundamentally
provide durable hierarhical indexing and distributed locking service.  The
locking service implements a capabilities that express what data and metadata
clients are allowed to access as well as what they may cache locally.  While
designed for a fixed file abstraction, indexing, locking, and caching are all
common services that are useful to large sets of applications.

@@

Because Lua is interpreted, it is also portable. The portability allows
functions to be shipped around the cluster without having to compile or
reason about compatibility issues. Traditionally, intefaces are written
in C/C++, so they must be compiled into shared libraries before being
injected into the daemon at runtime. Shared libraries need to be
compiled on the host they will be run on to accomodate different
architectures and dependendencies. Embedding the Lua interpretator, on
the other hand, gives us the flexbility to store the actual Lua code in
other places, like RADOS, so we can enjoy all the other properties
provided by that particular back-end.

@@

Dependencies, symbols, and functions specific to the object or balancer
interface are put in the \texttt{cls} or \texttt{bal} directories,
respectively. For example, the Lua object interface uses functions that
have placement group filters, cryptography functions, and object
metadata (\emph{it i.e.} \texttt{cxx\_omap\_getvals()}, object data,
object extended attributes, and object versions -- all these are
dependencies, symbols, and functions are part of the OSD process but not
the MDS process. As a result, we put interface code that uses these in
\texttt{cls} directory. With this scheme, The OSD will \texttt{dlopen()}
the shared library created by Lua object interface shared library while
the MDS will \texttt{dlopen()} the Lua balancer interface shared
library; both shared libraries will the Lua core.

@@

By leveraging the monitor daemons, our services get the consistency from
the monitors version management, the distribution from the monitors data
structures (which are already distributed), and the durability from the
robustness of the monitors and persistence with Paxos. The
implementation uses the placement group pool data structure which
maintains the policies (\emph{e.g.}, erasure coding) and organization
details (\emph{e.g.}, snapshots) for each pool. While stuffing the
information into the monitor map, the structure that describes the the
monitor topology, was an option, the placement group pool allows finer
grain control over different types of data.

@@

The zlog sequencer is volatile, shared resource that requires serialized
access. in corfu the sequencer is a fast, centeralized network counter
resource.

Initially we saught to directly model the sequencer in ceph as a non-exclusive,
non-cacheable resource, forcing clients to perform round-trip access the
resource at the authoratiave MDS for the inode representing the sequencer.
However, we found that the capapbility system in Ceph is used to batch access
to cacheable resources, providing clients best-effort access to the capability
and allowing them to burst. While unexpected, this alternative mode provides
a different approach to sequencer implementation.

>>>>

Auto-tuning techniques attempt to find a good solution among a huge space of
available system configurations. However, in practice auto-tuning is limited
to only the configuration tunables that the storage system exposes and can be
overwhelmed with too many parameters.  For instance, auto-tuning may be
capable of identifying instances in which new data layouts would benefit a
workload, but unless the system can provide such a transformation, the option
is left off the table.  Starfish~\cite{herodotou:cidr2011-starfish} made
an attempt of this for Hadoop but this technique would need to severely limit
the space of parameters in order to feasible, similar to the approach used in~\cite{behzad:sc2013-autotuning}.

@@

The distributed metadata service in Ceph provides clients with a POSIX file
system abstraction. Distributed file systems are complex, but fundamentally
provide durable hierarhical indexing and distributed locking service.  The
locking service implements capabilities that express what data and metadata
clients are allowed to access as well as what they may cache locally.  While
designed for a fixed file abstraction, indexing, locking, and caching are all
common services that are useful to large sets of applications.

@@

Because Lua is interpreted, it is also portable. The portability allows
functions to be shipped around the cluster without having to compile or
reason about compatibility issues. Traditionally, interfaces are written
in C/C++, so they must be compiled into shared libraries before being
injected into the daemon at runtime. Shared libraries need to be
compiled on the host they will be run on to accomodate different
architectures and dependendencies. Embedding the Lua interpretator, on
the other hand, gives us the flexbility to store the actual Lua code in
other places, like RADOS, so we can enjoy all the other properties
provided by that particular back-end.

@@

Dependencies, symbols, and functions specific to the object or balancer
interface are put in the \texttt{cls} or \texttt{bal} directories,
respectively. For example, the Lua object interface uses functions that
have placement group filters, cryptography functions, and object
metadata (\emph{it i.e.} \texttt{cxx\_omap\_getvals()}, object data,
object extended attributes, and object versions -- all these are
dependencies, symbols, and functions are part of the OSD process but not
the MDS process. As a result, we put interface code that uses these in
\texttt{cls} directory. With this scheme, the OSD will \texttt{dlopen()}
the shared library created by Lua object interface shared library while
the MDS will \texttt{dlopen()} the Lua balancer interface shared
library; both shared libraries will the Lua core.

@@

By leveraging the monitor daemons, our services get the consistency from
the monitors version management, the distribution from the monitors data
structures (which are already distributed), and the durability from the
robustness of the monitors and persistence with Paxos. The
implementation uses the placement group pool data structure which
maintains the policies (\emph{e.g.}, erasure coding) and organization
details (\emph{e.g.}, snapshots) for each pool. While stuffing the
information into the monitor map, the structure that describes the
monitor topology, was an option, the placement group pool allows finer
grain control over different types of data.

@@

The zlog sequencer is volatile, shared resource that requires serialized
access. In Corfu the sequencer is a fast, centeralized network counter
resource.

Initially we saught to directly model the sequencer in Ceph as a non-exclusive,
non-cacheable resource, forcing clients to perform round-trip access the
resource at the authoratiave MDS for the inode representing the sequencer.
However, we found that the capability system in Ceph is used to batch access
to cacheable resources, providing clients best-effort access to the capability
and allowing them to burst. While unexpected, this alternative mode provides
a different approach to sequencer implementation.
